 

### 2023-02-22 paper2.Rmd
Revising tables to improve readability
Addition of appendices, revisions throughout papers, acknowledgements

source("C:/Users/danie/Dropbox (Harvard University)/madagascar_mh/code/0_a_packages_and_paremeters_do_file.R")

@@

load(file = paste(resultspath,"3_climate", 
                  "climate_facilities.Rdata", sep = "/"))

@@

n_facilities_sm <- data_climate %>% 
  filter(date == "Jan 2010") %>%
  dplyr::select(sm_monthly, facility_ID) %>%
  filter(!is.na(sm_monthly)) %>%
  dplyr::select(facility_ID) %>%
  unique() %>%
  nrow()

n_facilities_sm_missing <- data_climate %>% 
  filter(date == "Jan 2010") %>%
  dplyr::select(sm_monthly, facility_ID) %>%
  filter(is.na(sm_monthly)) %>%
  dplyr::select(facility_ID) %>%
  unique() %>%
  nrow()

@@

To address heterogeneity in reporting, our analysis aggregated any monthly incidence of mental or neurological disorders reported by a facility, irrespective of age and sex, into a summary outcome measure. To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series. The nonparametric Friedman’s super smoother regression estimator[@friedmanVariableSpanScatterplot1984] was applied to each time series to identify outlier observations and replace them through linear interpolation.[@hyndmanAutomaticTimeSeries2008] By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may reflect true variances in incidence (for example, incidences reported by a large, regional reference hospital) while addressing potential errors in data entry. (Additional detail on the data cleaning process is available in the Supplementary appendix.)

@@

First, region, district, and commune names in our sample were standardized against reference shapefiles to address variations in translation, abbreviation, transposition, accent marks, spacing, hyphenation, and spelling. (A summary of the standardized names is provided in the Supplementary appendix.) Next, facility names, types, and associated administrative units were used to match facilities to a validated spatial inventory of health facilities in Sub-Saharan Africa,[@mainaSpatialDatabaseHealth2019] of which `r format(as.numeric(n_facilities_who), big.mark = ",")` coordinates were provided for public facilities in Madagascar. In order to systematically match facilities in our sample to facilities in the spatial inventory, we implemented approximate string matching, which allowed for facility names and administrative units to be matched approximately, rather than exactly, to corresponding patterns in the validated spatial inventory. Applying this matching technique, `r format(as.numeric(n_matched_facilities), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities)/num_facilities * 100,0)`%) in our sample were matched to validated coordinates.

@@

To gauge the accuracy of the geolocating process, a subset of 1% of geolocated facilities was selected for validation against manually identified coordinates. Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(as.numeric(validation_mean_dist),2), big.mark = ",")` km., with a maximum distance of approximately `r format(round(as.numeric(validation_max_dist), 1), big.mark = ",")` kilometers, indicating high accuracy in the geolocated process relative to the spatial resolution of climate data. Additional detail on the geolocating and validation process is available in the Supplementary appendix.

@@

Our primary analysis involved conducting four models to estimate the association between facility-level counts of incident mental disorders and climate conditions. Model 1 used temperature as the principal predictor of counts of incident mental disorders. Model 2 only used soil moisture as a predictor. Model 3 used both temperature and soil moisture independently as predictors, while Model 4—our preferred model—introduced an interaction term between the two. 
Duration of cyclone activity was included in all models using our count indicator of exposure. In all models, we included fixed effects for Madagascar’s twenty-two regions to account for geographic differences in climate patterns and case reporting. We further included month and year fixed effects to account for seasonality and time-varying omitted variables.

@@

panel_a <- data_climate %>%
  filter(statistic == e) %>%
  dplyr::select(date, facility_ID, temp_monthly) %>%
  unique() %>%
  inner_join(., facilities_all_gps) %>%
  dplyr::select(date, geometry, facility_ID, temp_monthly) %>%
  filter(date == "Jan 2015" | date == "June 2015" ) %>%
  mutate(date_2 = ifelse(date == "Jan 2015", "January 2015", "June 2015")) %>%
  filter(!is.na(date_2)) %>%
  ggplot(aes(geometry=geometry)) +
  # geom_sf(data = map_mdg_3_un,
  #         size = 0.2,
  #         color = col_grey_light,
  #         fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = "grey40",
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_lightest) +
  # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
  geom_sf(alpha = 0.9, size = .7, aes(color = temp_monthly)) +
  theme_void() +
  # scale_alpha(range = c(0,1)) +
  scale_color_viridis(option = "magma") +
  labs(color = "Temperature ( ̊ C)") +
  theme(text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")) +
  facet_wrap(~date_2)

panel_b <-  data_climate %>%
  filter(statistic == e) %>%
  dplyr::select(date, facility_ID, sm_monthly) %>%
  unique() %>%
  inner_join(., facilities_all_gps) %>%
  dplyr::select(date, geometry, facility_ID, sm_monthly) %>%
  filter(date == "Jan 2015" | date == "June 2015" ) %>%
  mutate(date_2 = ifelse(date == "Jan 2015", "January 2015", "June 2015")) %>%
  filter(!is.na(date_2)) %>%
  ggplot(aes(geometry=geometry)) +
  # geom_sf(data = map_mdg_3_un,
  #         size = 0.2,
  #         color = col_grey_light,
  #         fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = "grey40",
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_lightest) +
  # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
  geom_sf(alpha = 0.9, size = .9, aes(color = sm_monthly)) +
  theme_void() +
  # scale_alpha(range = c(0,1)) +
  scale_color_viridis(option = "mako", direction = -1) +
  labs(color = "Soil moisture (%)") +
  theme(text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")) +
  facet_wrap(~date_2)

@@

panel_a <- data_climate %>%
  mutate(date = as.yearmon(date),
         year = as.factor(year(date)),
         month = month(date)) %>%
  filter(year != "2022") %>%
  ggplot(aes(x=temp_monthly, y = year, fill = stat(x))) +
  geom_density_ridges_gradient() +
  labs(x = "Temperature ( ̊ C)",
       title = "A:",
       y = "Year") +
  theme_classic() +
  theme(text = element_text(family = "Source Sans Pro"),
        legend.position = "") +
  scale_fill_viridis(option = "magma")

panel_b <- data_climate %>%
  mutate(date = as.yearmon(date),
         year = as.factor(year(date)),
         month = month(date)) %>%
  filter(year != "2022") %>%
  ggplot(aes(x=sm_monthly, y = year, fill = stat(x))) +
  geom_density_ridges_gradient() +
  labs(x = "Soil moisture (%)",
       title = "B:",
       y = "Year") +
  theme_classic() +
  theme(text = element_text(family = "Source Sans Pro"),
        legend.position = "") +
  scale_fill_viridis(option = "mako", direction = -1)

# panel_a <- data_climate %>%
#   mutate(date = as.yearmon(date),
#          year = as.factor(year(date)),
#          month = month(date)) %>%
#   filter(year != "2022") %>%
#   ggplot(aes(x=temp_monthly, group = year, fill = year, color = year)) +
#   geom_density(alpha=0.45, position="identity") +
#   labs(x = "Temperature ( ̊ C)",
#        title = "A:",
#        y = "Density",
#        fill = "Year",
#        color = "Year") +
#   theme_classic() +
#   theme(text = element_text(family = "Source Sans Pro")) +
#   scale_color_viridis(discrete = TRUE, option = "magma") +
#   scale_fill_viridis(discrete = TRUE, option = "magma")
#
# panel_b <- data_climate %>%
#   mutate(date = as.yearmon(date),
#          year = as.factor(year(date)),
#          month = month(date)) %>%
#   filter(year != "2022") %>%
#   ggplot(aes(x=sm_monthly, group = year, fill = year, color = year)) +
#   geom_density(alpha=0.45, position="identity") +
#   labs(x = "Soil moisture (%)",
#        title = "B:",
#        y = "Density",
#        fill = "Year",
#        color = "Year") +
#   theme_classic() +
#   theme(text = element_text(family = "Source Sans Pro")) +
#   scale_color_viridis(discrete = TRUE, option = "mako") +
#   scale_fill_viridis(discrete = TRUE, option = "mako")

@@

@@

rm(packages_and_paremeters_on)

>>>>

# Loading libraries
# library(MASS) # We load this and then detach it just to clear the package
# library(margins) # We load this and then detach it just to clear the package
# library(lme4) # We load this and then detach it just to clear the package
# detach("package:lme4", unload=TRUE) # Needed to use dplyr's select function
# detach("package:margins", unload=TRUE) # Needed to use dplyr's select function
# detach("package:MASS", unload=TRUE) # Needed to use dplyr's select function
library(readxl)
library(readr)
library(dplyr)
library(zoo)
library(tidyr)
library(psych)
library(ggplot2)
library(RColorBrewer)
library(sp)
library(broom)
library(sf)
library(scales)
library(viridis)
library(data.table)
library(ggpubr)
library(ggmap)
library(maps)
library(mapdata)
library(ggrepel)
library(table1)
library(stringr) 
library(stringi)
library(fixest)
library(stats)
library(lubridate)
library(forecast)
library(gtools)
# library(devtools)
library(reticulate)
library(stargazer)
library(lwgeom)
if (!require("ggsflabel")) devtools::install_github("yutannihilation/ggsflabel")
library(openxlsx)
library(gganimate)
library(transformr)
library(huxtable)
library(ggtext)
library(margins)
library(ncdf4) # package for netcdf manipulation
library(magrittr)
library(lmtest)
library(sandwich)
library(rgee)
library(gt)
library(knitr)
library(webshot2)
library(sysfonts)
library(showtext)
font_add_google("Source Sans Pro")
library(gridExtra)
library(tibble)
showtext_auto() 
showtext_opts(dpi = 300)  
# library(googledrive)
# drive_auth(email = TRUE)
library(rmdHelpers)
library(gtExtras)
library(kableExtra)
library(DescTools)
library(rvest)
library(httr)
library(polite)
library(janitor)
library(cowplot)
library(ggridges)
# library(ggsn)

# library(glmmTMB)

# Setting directories - change these to your local directory
path <- 'C:/Users/danie/Dropbox (Harvard University)/madagascar_mh'
code <- paste(path,'code', sep = "/")
path_python  = "C:/Users/danie/AppData/Local/Programs/Python/Python310/python.exe"

# Data
datasource <- paste('C:/Users/danie/Dropbox (Harvard University)/data',
                    sep = "/") # The complete data set is not uploaded to 
# Github. Ask golden@hsph.harvard.edu for access. 
datapath <- paste(path,'data', sep = "/")
datapath_reference  <- paste(datapath,'0_reference', sep = "/")
data_mh_chd  <- paste(datapath,'1_mental_health', sep = "/")
data_mh_csb <- data_mh_chd  
data_mh_chu_chrr <- paste(data_mh_chd,'pathologies neuropsychiatriques CHU CHRR', sep = "/")
data_gps <- paste(datapath,'2_gps', sep = "/")
data_gps_sources <- paste(data_gps,'gps_sources', sep = "/")
data_gps_sources_searches <- paste(data_gps_sources,'searches', sep = "/")
data_gps_sources_reposit <- paste(data_gps_sources,'repositories', sep = "/")
data_climate_path  <- paste(datapath,'3_climate', sep = "/")
data_climate_era  <- paste(data_climate_path,'ERA5', sep = "/")
data_climate_esa  <- paste(data_climate_path,'ESA_CCI', sep = "/")

# Results
resultspath <- paste(path,'results', sep = "/")
mh_path <- paste(resultspath,'1_mental_health', sep = "/")
gpspath <- paste(resultspath,'2_gps', sep = "/")
gpspath_admin_names <- paste(gpspath,'0_reference', sep = "/")
gpspath_fig <-  paste(gpspath,'1_figures', sep = "/")
gpspath_spread <-  paste(gpspath,'2_spreadsheets', sep = "/")
gpspath_spread_fuzzy <-  paste(gpspath_spread,'3_fuzzy_matching', sep = "/")
analysispath <- paste(resultspath,'4_analysis', sep = "/")
analysis_figures <- paste(analysispath,'1_figures', sep = "/")
analysis_models <- paste(analysispath,'3_models', sep = "/")

# Shapefiles
mappath <- paste(path,'shapefiles', sep = "/")
mappath_MOH <- paste(mappath,'MOH', sep = "/")
mappath_OCHA <- paste(mappath,'OCHA', sep = "/")

# Color palette 
col_light = "cyan4"
col_dark = "cyan3"
col_bright = "coral"
col_black = "black"
col_grey_dark = "grey20"
col_grey_med = "grey40"
col_grey_light = "grey80"
col_grey_lightest = "grey85"
col_soilmoisture = col_dark
col_temperature = col_light
col_interaction = col_bright
col_cyclone = "steelblue2"

pal <- c("lightskyblue2", "steelblue2", "dodgerblue2", "dodgerblue3", "dodgerblue4", "darkblue")

col_within_threshold = "cyan3"
col_beyond_threshold = "coral"

col_centroid <- "grey20"
col_exact_all <- "cyan2"
col_exact_rhino <- "cyan3"
col_exact_val <- "cyan4"
col_search <- "coral"

col_CH <- "coral"
col_CHD <- "coral1"
col_CHR <- "coral3"
col_CSB <- "steelblue2"
col_CSB1 <- "steelblue1"
col_CSB2 <- "steelblue3"
col_other <-  "grey20"

col_model_main <- "#F3AB00"
col_model_other <- col_grey_med
col_spec_yes <-  "#73BDBF"
col_spec_no <-  "white"

col_cases <- "chartreuse3"
col_no_cases <- "deeppink3"

col_eco_rainforest <-"#32A42F"
col_eco_highlands <- "#B9CF19"
col_eco_arid <- "#FEEE19"
col_eco_drydecid <- "#FCAF3E"

# Thresholds
# These are cut off values that will be used in the GPS do file

length_lim <- 15  # The maximum distance allowed when the same facility has
# two GPS coordinates in the data sources for the center of
# those two coordinates to be used as the facility's location.
# Note: the selection of 15 is arbitrarily conservative. Spatial resolution of 
# climate data is typically ~ 30km x 30 km

area_lim <- length_lim*length_lim

# The maximum area of the convex hull allowed when the same facility has
# 3+ GPS coordinates in the data sources for the centroid of
# that convex hull to be used as the facility's location

fokontany_lim <- area_lim    # A small fokotanty is one that is ____ km ^2 or smaller

commune_lim <- area_lim    # A small commune is one that is ____ km ^2 or smaller

# Lags: specify how many lags you want for the explanatory variables (e.g., soil moisture, temp)

lags_number <- 18

# Climate data start and end date
start_date <- as.Date("2010-01-01")
end_date <- as.Date("2020-07-01")

start_date_climate <- start_date - lags_number*31 #This ensures there is data for the lagged exposure
end_date_climate <- end_date

# ESA CCI trim dates
date1 <- 200801
date2 <- 202112

# Seed and sampling fraction
set.seed(1960) # Madgascar's year of independence
sample_fraction = .01

######################
##      MAPS        ##
######################
#   
# # There are two map options available. One set of shapefiles were available
# # from humdata.org, while the other set was provided by the MOH.
#   
# # Loading high-resolution maps of St. Lucia (from data.humdata.org)
map_mdg_0_un <- st_read(paste0(mappath_OCHA,"/",
                               "mdg_admbnda_adm0_BNGRC_OCHA_20181031.shp"))
map_mdg_1_un <- st_read(paste0(mappath_OCHA,"/",
                               "mdg_admbnda_adm1_BNGRC_OCHA_20181031.shp"))
map_mdg_2_un <- st_read(paste0(mappath_OCHA,"/",
                               "mdg_admbnda_adm2_BNGRC_OCHA_20181031.shp"))
map_mdg_3_un <- st_read(paste0(mappath_OCHA,"/",
                               "mdg_admbnda_adm3_BNGRC_OCHA_20181031.shp"))
loaded_maps_un <- 1

# Load in data from MOH
map_mdg_0 <- st_read(paste0(mappath_MOH,"/",
                            "adm0_mada_utm38S.shp"))
map_mdg_1 <- st_read(paste0(mappath_MOH,"/",
                            "adm1_mada_utm38S.shp"))
map_mdg_2 <- st_read(paste0(mappath_MOH,"/",
                            "adm2_mada_utm38S.shp"))
map_mdg_3 <- st_read(paste0(mappath_MOH,"/",
                            "adm3_mada_utm38S.shp"))
map_mdg_4 <- st_read(paste0(mappath_MOH,"/",
                            "adm4_mada_utm38S.shp"))

@@

load(file = paste(resultspath,"3_climate", 
                  "climate_facilities_subset.Rdata", sep = "/"))

@@

n_facilities_sm <- data_climate_subset %>% 
  filter(date == "Jan 2010") %>%
  dplyr::select(sm_mean, facility_ID) %>%
  filter(!is.na(sm_mean)) %>%
  dplyr::select(facility_ID) %>%
  unique() %>%
  nrow()

n_facilities_sm_missing <- data_climate_subset %>% 
  filter(date == "Jan 2010") %>%
  dplyr::select(sm_mean, facility_ID) %>%
  filter(is.na(sm_mean)) %>%
  dplyr::select(facility_ID) %>%
  unique() %>%
  nrow()

@@

To address heterogeneity in reporting, our analysis aggregated any monthly incidence of mental or neurological disorders reported by a facility, irrespective of age and sex, into a summary outcome measure. To address outliers, monthly observations of the outcome were arranged separately for each facility into a unique time series. The nonparametric Friedman’s super smoother regression estimator[@friedmanVariableSpanScatterplot1984] was applied to each time series to identify outlier observations and replace them through linear interpolation.[@hyndmanAutomaticTimeSeries2008] By considering outliers on a facility-by-facility basis, the data cleaning approach preserved extreme values that may reflect true variances in incidence (for example, incidences reported by a large, regional reference hospital) while addressing potential errors in data entry. (Additional detail on the data cleaning process is available in Appendix 2.1)

@@

First, region, district, and commune names in our sample were standardized against reference shapefiles to address variations in translation, abbreviation, transposition, accent marks, spacing, hyphenation, and spelling. (A summary of the standardized names is provided in Appendix 2.2.) Next, facility names, types, and associated administrative units were used to match facilities to a validated spatial inventory of health facilities in Sub-Saharan Africa,[@mainaSpatialDatabaseHealth2019] of which `r format(as.numeric(n_facilities_who), big.mark = ",")` coordinates were provided for public facilities in Madagascar. In order to systematically match facilities in our sample to facilities in the spatial inventory, we implemented approximate string matching, which allowed for facility names and administrative units to be matched approximately, rather than exactly, to corresponding patterns in the validated spatial inventory. Applying this matching technique, `r format(as.numeric(n_matched_facilities), big.mark = ",")` facilities (`r round(as.numeric(n_matched_facilities)/num_facilities * 100,0)`%) in our sample were matched to validated coordinates.

@@

To gauge the accuracy of the geolocating process, a subset of 1% of geolocated facilities was selected for validation against manually identified coordinates. Comparing the geolocated coordinates to validated coordinates for each facility, the mean distance between coordinates in the validation sample was `r format(round(as.numeric(validation_mean_dist),2), big.mark = ",")` km., with a maximum distance of approximately `r format(round(as.numeric(validation_max_dist), 1), big.mark = ",")` kilometers, indicating high accuracy in the geolocated process relative to the spatial resolution of climate data. Additional detail on the geolocating and validation process is available in Appendix 2.2.

@@

Our primary analysis involved conducting four models to estimate the association between facility-level counts of incident mental disorders and climate conditions. Model 1 used temperature as the principal predictor of counts of incident mental disorders. Model 2 only used soil moisture as a predictor. Model 3 used both temperature and soil moisture independently as predictors, while Model 4—our preferred model—introduced an interaction term between the two.

Duration of cyclone activity was included in all models using our count indicator of exposure. In all models, we included fixed effects for Madagascar’s twenty-two regions to account for geographic differences in climate patterns and case reporting. We further included month and year fixed effects to account for seasonality and time-varying omitted variables.

@@

panel_a <- data_climate_subset %>%
  dplyr::select(date, facility_ID, mean_2m_air_temperature) %>%
  unique() %>%
  inner_join(., facilities_all_gps) %>%
  dplyr::select(date, geometry, facility_ID, mean_2m_air_temperature) %>%
  filter(date == "Jan 2015" | date == "June 2015" ) %>%
  mutate(date_2 = ifelse(date == "Jan 2015", "January 2015", "June 2015")) %>%
  filter(!is.na(date_2)) %>%
  ggplot(aes(geometry=geometry)) +
  # geom_sf(data = map_mdg_3_un,
  #         size = 0.2,
  #         color = col_grey_light,
  #         fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = "grey40",
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_lightest) +
  # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
  geom_sf(alpha = 0.9, size = .7, aes(color = mean_2m_air_temperature)) +
  theme_void() +
  # scale_alpha(range = c(0,1)) +
  scale_color_viridis(option = "magma") +
  labs(color = "Temperature ( ̊ C)") +
  theme(text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")) +
  facet_wrap(~date_2)

panel_b <-  data_climate_subset %>%
  dplyr::select(date, facility_ID, sm_mean) %>%
  unique() %>%
  inner_join(., facilities_all_gps) %>%
  dplyr::select(date, geometry, facility_ID, sm_mean) %>%
  filter(date == "Jan 2015" | date == "June 2015" ) %>%
  mutate(date_2 = ifelse(date == "Jan 2015", "January 2015", "June 2015")) %>%
  filter(!is.na(date_2)) %>%
  ggplot(aes(geometry=geometry)) +
  # geom_sf(data = map_mdg_3_un,
  #         size = 0.2,
  #         color = col_grey_light,
  #         fill = NA) +
  geom_sf(data = map_mdg_2_un,
          size = 0.2,
          color = "grey40",
          fill = NA) +
  geom_sf(data = map_mdg_1_un,
          size = 0.2,
          color = col_black,
          fill = NA) +
  # geom_sf_text(data = map_mdg_1_un, aes(label = ADM1_EN),
  #              size = 2, color = col_grey_lightest) +
  # geom_sf(alpha = 0.1, size = 5, aes(color = temp_monthly)) +
  geom_sf(alpha = 0.9, size = .9, aes(color = sm_mean)) +
  theme_void() +
  # scale_alpha(range = c(0,1)) +
  scale_color_viridis(option = "mako", direction = -1) +
  labs(color = "Soil moisture (%)") +
  theme(text = element_text(family = "Source Sans Pro"),
        strip.background = element_rect(colour="white",
                                        fill="white")) +
  facet_wrap(~date_2)

@@

panel_a <- data_climate_subset %>%
  mutate(date = as.yearmon(date),
         year = as.factor(year(date)),
         month = month(date)) %>%
  filter(year != "2022") %>%
  ggplot(aes(x=mean_2m_air_temperature, y = year, fill = stat(x))) +
  geom_density_ridges_gradient() +
  labs(x = "Temperature ( ̊ C)",
       title = "A:",
       y = "Year") +
  theme_classic() +
  theme(text = element_text(family = "Source Sans Pro"),
        legend.position = "") +
  scale_fill_viridis(option = "magma")

panel_b <- data_climate_subset %>%
  mutate(date = as.yearmon(date),
         year = as.factor(year(date)),
         month = month(date)) %>%
  filter(year != "2022") %>%
  ggplot(aes(x=sm_mean, y = year, fill = stat(x))) +
  geom_density_ridges_gradient() +
  labs(x = "Soil moisture (%)",
       title = "B:",
       y = "Year") +
  theme_classic() +
  theme(text = element_text(family = "Source Sans Pro"),
        legend.position = "") +
  scale_fill_viridis(option = "mako", direction = -1)

# panel_a <- data_climate_subset %>%
#   mutate(date = as.yearmon(date),
#          year = as.factor(year(date)),
#          month = month(date)) %>%
#   filter(year != "2022") %>%
#   ggplot(aes(x=temp_monthly, group = year, fill = year, color = year)) +
#   geom_density(alpha=0.45, position="identity") +
#   labs(x = "Temperature ( ̊ C)",
#        title = "A:",
#        y = "Density",
#        fill = "Year",
#        color = "Year") +
#   theme_classic() +
#   theme(text = element_text(family = "Source Sans Pro")) +
#   scale_color_viridis(discrete = TRUE, option = "magma") +
#   scale_fill_viridis(discrete = TRUE, option = "magma")
#
# panel_b <- data_climate_subset %>%
#   mutate(date = as.yearmon(date),
#          year = as.factor(year(date)),
#          month = month(date)) %>%
#   filter(year != "2022") %>%
#   ggplot(aes(x=sm_monthly, group = year, fill = year, color = year)) +
#   geom_density(alpha=0.45, position="identity") +
#   labs(x = "Soil moisture (%)",
#        title = "B:",
#        y = "Density",
#        fill = "Year",
#        color = "Year") +
#   theme_classic() +
#   theme(text = element_text(family = "Source Sans Pro")) +
#   scale_color_viridis(discrete = TRUE, option = "mako") +
#   scale_fill_viridis(discrete = TRUE, option = "mako")

@@

\begin{spacing}{1.5}

@@

rm(packages_and_paremeters_on, data_climate, data_climate_subset, map_mdg_0, map_mdg_0_un,
   map_mdg_1, map_mdg_1_un, map_mdg_2, map_mdg_2_un)
